Figures

### 2019-05-20 figures/08_exploratory_dotplot.Rmd
prettyfi dotplot labels

prep_dotplot <- function(x, col_name){
  dplyr::select(x, UQ(rlang::sym(col_name))) %>% 
    dplyr::mutate(var = factor(row.names(x), 
                            levels = rev(row.names(x)))) %>%
    dplyr::filter(!(var %in% c("tp", "tn")))
}

plot_opts <- theme(axis.title.y = element_blank(), 
                   axis.text = element_text(size = 8))
plot_grid(
  ggplot(data = prep_dotplot(dt_tp, "tp")) + 
    geom_point(aes(x = tp, y = var)) + 
    plot_opts, 
  ggplot(data = prep_dotplot(dt_tn, "tn")) + 
    geom_point(aes(x = tn, y = var)) +
    plot_opts
)

>>>>

prep_dotplot <- function(x, col_name){
  pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
  res      <- dplyr::select(x, UQ(rlang::sym(col_name))) %>%

    dplyr::mutate(var = row.names(x)) %>%
    dplyr::left_join(pred_key, by = "var") %>%
    dplyr::mutate(var = factor(row.names(x), 
                            levels = rev(row.names(x))), 
                  pretty = factor(pretty, levels = rev(pretty)),
                  category = factor(category, 
                                    levels = c("Lake", "Nutrient sources",
                                               "Nutrient proxies",
                                               "Transport capacity"))) %>%
    dplyr::filter(!(var %in% c("tp", "tn")))
  res
}

plot_opts <- theme(axis.title.y = element_blank(), 
                   axis.text = element_text(size = 8), 
                   legend.position = 0)

# head(prep_dotplot(dt_tp, "tp"))
# show_col(brewer_pal("div", "Set1")(4))                   
gg_tp <-  ggplot(data = prep_dotplot(dt_tp, "tp")) + 
    geom_point(aes(x = tp, y = pretty, color = category)) + 
    scale_color_brewer(palette = "Set1") +
    xlim(0, 0.5) +
    plot_opts
gg_tn <- ggplot(data = prep_dotplot(dt_tn, "tn")) + 
    geom_point(aes(x = tn, y = pretty, color = category)) +
    scale_color_brewer(palette = "Set1") +
    xlim(0, 0.5) +
    plot_opts
legend_b <- get_legend(gg_tp + 
                         theme(legend.position="bottom", 
                               legend.justification = "center", 
                               legend.text = element_text(size = 10), 
                               legend.title = element_blank()))
plot_grid(
  plot_grid(gg_tp, gg_tn), 
  legend_b, ncol = 1, rel_heights = c(1, 0.1))
